\let\nofiles\relax
\documentclass[margin,line]{res}

\usepackage{xcolor}

\usepackage[greek, english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[hidelinks, colorlinks=true,allcolors=blue]{hyperref}
\usepackage{tikz}
%\usepackage{titlesec}

\newcommand{\g}{\textgreek}
\newcommand{\ver}{\vspace*{-2.7mm}}
\renewcommand{\baselinestretch}{1.0}
%\renewcommand{\baselineskip}{1.5in}

\oddsidemargin -0.7in
\evensidemargin -.7in
\textwidth=6.2in
\textheight=690pt
\voffset=-0.4in
\hoffset=1.4in
\itemsep=0in
\parsep=0in
% if using pdflatex:
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
\newenvironment{list3}{
  \begin{list}{}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
\definecolor{urlblue}{HTML}{0000EE}


\begin{document}

\name{ Yizhe Xu - CV  \hspace{17em} {\normalfont \textit{Last update: \today}}\vspace*{.1in}}

\begin{resume}
\section{\sc Contact Details}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{4in}}
Stanford University             & {Telephone:}  +1 (801) 433-7346 \\
\href{https://bmir.stanford.edu}{Center for Biomedical Informatics Research}  & {E-mail:}    yizhex@stanford.edu \\
1265 Welch Road, &  {Website:} \href{https://crystalxur.github.io/}{https://crystalxur.github.io/}\\
Stanford, CA 94305, USA  & {Google Scholar:} \href{https://scholar.google.com/citations?view_op=list_works&hl=en&user=_H8BKfMAAAAJ}{user=\_H8BKfMAAAAJ} \\
\end{tabular}



\section{\sc Research Interests}
I am interested in causal inference, semiparametric and nonparametric statistics, and machine learning methods. I am passionate about applying advanced methods in statistics and machine learning to answer meaningful questions in biomedical research. My recent research has focused on the estimation of heterogeneous treatment effects in clinical trials or observational studies and identification of individualized treatment rules.

\section{\sc Education}
{\bf Stanford University} \hfill Stanford, California, USA\\
\vspace*{-.14in}
\begin{list2}
\item
\textbf{Postdoctoral fellow in Biomedical Informatics.} \hfill  08/2020 -- present\\
Advisor: Nigam Shah
\end{list2}

{\bf {University of Utah}} \hfill  {Salt Lake City, Utah, USA}\\
\vspace*{-.14in}
\begin{list2}
\item
\textbf{Ph.D. in Population Health Sciences. (Emphasis in Biostatistics)} \hfill  08/2016 -- 08/2020\\
Thesis advisor: Jincheng Shen and Tom Greene\\
Thesis title: Estimating the optimal individualized treatment rule from a cost-effectiveness perspective.
\item \textbf{M.Sc. Statistics} \hfill 2014 - 2016\\
Thesis advisors: Nan Hu 
\end{list2}

{\bf {Liaoning Medical University}} \hfill  {Liaoning, China}\\
\vspace*{-.14in}
\begin{list2}
\item \textbf{B.Sc. Nursing} \hfill 2008 - 2012\\
\end{list2}


\section{\sc Awards}
\textbf{Joint Statistical Meeting, Student Paper Award} \hfill 2021\\
Health Policy Statistics Section, Virtual Conference \\
\textbf{American Statistical Association, Student Travel Award} \hfill 2019\\
Biopharmaceutical Section Regulatory-Industry Statistics Workshop Program, Washington D.C., USA.  \\
\textbf{Student of the Year}, Master of Statistics, University of Utah. \hfill 2017\\
\textbf{Phi Kappa Phi Inductee}, Division of Public Health, University of Utah. \hfill 2017 \\
\textbf{Student of the Year}, Liaoning Medical University. \hfill 2011\\

\section{\sc Journal Publications}
\begin{list1}
\item[1.] Xu, Y., Greene, T.H., Bress, A.P., Sauer, B.C., Bellows, B.K., Zhang, Y., Weintraub, W.S., Moran, A.E. and Shen, J. (2022). \textbf{Estimating the optimal individualized treatment rule from a cost-effectiveness perspective.} Biometrics, 78(1), pp.337-351. 
\item[2.] Xu, Y., Greene, T.H., Bress, A.P., Bellows, B.K., Zhang, Y., Zhang, Z., Kolm, P., Weintraub, W.S., Moran, A.S. and Shen, J. (2022). \textbf{An Efficient Approach for Optimizing the Cost-effective Individualized Treatment Rule Using Conditional Random Forest.} Statistical Methods in Medical Research (forthcoming).
\item[3.] Pfohl, S.R., Zhang, H., Xu, Y., Foryciarz, A., Ghassemi, M. and Shah, N.H. (2022). \textbf{A comparison of approaches to improve worst-case predictive model performance over patient subpopulations.} Scientific reports, 12(1), pp.1-13. 
\item[4.] Bress, A.P., Greene, T., Derington, C.G., Shen, J., Xu, Y., Zhang, Y., Ying, J., Bellows, B.K., Cushman, W.C., Whelton, P.K. and Pajewski, N.M. (2021). \textbf{Patient selection for intensive blood pressure management based on benefit and adverse events.} Journal of the American College of Cardiology, 77(16), pp.1977-1990. 
\item[5.] Corbett, K.L., Presson, A.P., Zhang, C., Xu, Y., Bratton, S.L. and Dixon, R.R. (2021). \textbf{Does Non-Neurologic Multiorgan Dysfunction After Out-of-Hospital Cardiac Arrest among Children Admitted in Coma Predict Outcome 1 Year Later?} Journal of Pediatric Intensive Care, 10(03), pp.188-196. 
\item[6.] Sauer, B.C., Chen, W., Xu, Y., Shen, J., Accortt, N.A., Collier, D.H. and Cannon, G.W. (2020). \textbf{Empirical evidence of disease activity thresholds used to indicate need for major therapeutic change in US veterans with rheumatoid arthritis.} Arthritis research & therapy, 22(1), pp.1-10. 
\item[7.] Bailey, T.L., Stephens, A.R., Adeyemi, T.F., Xu, Y., Presson, A.P., Aoki, S.K. and Maak, T.G. (2019). \textbf{Traction time, force and postoperative nerve block significantly influence the development and duration of neuropathy following hip arthroscopy.} Arthroscopy: The Journal of Arthroscopic & Related Surgery, 35(10), pp.2825-2831. 
\item[8.] Lucas*, J., Myers, J., Keihani, S., Moses, R., Xu, Y., Morris, B., Majercik, S., Hewitt, T., Burks, F., Schwartz, I. and Elliott, S. (2019). \textbf{MP04-03 Treatment Complications Associated with Extraperitoneal Bladder Injuries: Results from the Multi-Institutional AAST Study of Bladder Trauma.} The Journal of Urology, 201(Supplement 4), pp.e30-e31. 
\item[9.] Kazmers, N.H., Stephens, A.R., Presson, A.P., Xu, Y., Feller, R.J. and Tyser, A.R. (2019). \textbf{Comparison of direct surgical costs for proximal row carpectomy and four-corner arthrodesis.} Journal of Wrist Surgery, 8(01), pp.066-071. 
\item[10.] Bailey, T., Maak, T.G., Stephens, A., Adeyemi, T., Xu, Y. and Presson, A. (2018). \textbf{The Association of Traction Time, Force and Postoperative Nerve Block on the Development and Duration of Neuropathy Following Hip Arthroscopy.} Arthroscopy, 34(12), p.e18. 
\item[11.] Kazmers, N.H., Presson, A.P., Xu, Y., Howenstein, A. and Tyser, A.R. (2018). \textbf{Cost implications of varying the surgical technique, surgical setting, and anesthesia type for carpal tunnel release surgery.} The Journal of hand surgery, 43(11), pp.971-977. 
\item[12.] Kazmers, N.H., Stephens, A., Presson, A.P., Xu, Y., Feller, R.J. and Tyser, A. (2018). \textbf{Comparison of Direct Surgical Costs for Proximal Row Carpectomy and 4-Corner Arthrodesis: Level 3 Evidence.} Journal of Hand Surgery, 43(9), p.S52. 
\item[13.] Kazmers, N.H., Judson, C.H., Presson, A.P., Xu, Y. and Tyser, A.R. (2018). \textbf{Evaluation of factors driving cost variation for distal radius fracture open reduction internal fixation.} The Journal of hand surgery, 43(7), pp.606-614. 
\item[14.] Kwok, A.C., Edwards, K., Donato, D.P., Tatro, E., Xu, Y., Presson, A.P. and Agarwal, J.P. (2018). \textbf{Operative time and flap failure in unilateral and bilateral free flap breast reconstruction.} Journal of Reconstructive Microsurgery, 34(06), pp.428-435. 
\item[15.] Pirozzi, C.S., Mendoza, D.L., Xu, Y., Zhang, Y., Scholand, M.B. and Baughman, R.P. (2018). \textbf{Short-term particulate air pollution exposure is associated with increased severity of respiratory and quality of life symptoms in patients with fibrotic sarcoidosis.} International journal of environmental research and public health, 15(6), p.1077. 
\item[16.] Workman, J.K., Wilkes, J., Presson, A.P., Xu, Y., Heflin, J.A. and Smith, J.T. (2018). \textbf{Variation in adolescent idiopathic scoliosis surgery: implications for improving healthcare value.} The Journal of pediatrics, 195, pp.213-219. 
\item[17.] Keihani, S., Moses, R., Xu, Y., Putbrese, B., Rogers, D., Luo-Owen, X., Mukherjee, K., Morris, B., Majercik, S., Piotrowski, J. and Dodgion, C. (2018). \textbf{MP25-18 Imaging Findings Associated with Renal Bleeding Interventions after High-grade Trauma: Results from the American Association for Surgery of Trauma (AAST) Genito-urinary Trauma Study.} The Journal of Urology, 199(4S), pp.e333-e334. 
\item[18.] Keihani, S., Xu, Y., Presson, A.P., Hotaling, J.M., Nirula, R., Piotrowski, J., Dodgion, C.M., Black, C.M., Mukherjee, K., Morris, B.J. and Majercik, S. (2018). \textbf{Contemporary management of high-grade renal trauma: Results from the American Association for the Surgery of Trauma Genitourinary Trauma study.} Journal of Trauma and Acute Care Surgery, 84(3), pp.418-425. 
\item[19.] Corbett, K., Xu, Y., Presson, A., Bratton, S. and Dixon, R. (2018). \textbf{Multiple Organ Dysfunction Prevalence Following Out-of-hospital Cardiac Arrest in Pediatrics.} Critical Care Medicine, 46(1), p.220. 
\item[20.] Awad, A.W., Karsy, M., Sanai, N., Spetzler, R., Zhang, Y., Xu, Y. and Mahan, M.A. (2017). \textbf{Impact of removed tumor volume and location on patient outcome in glioblastoma.} Journal of neuro-oncology, 135(1), pp.161-171. 
\item[21.] Matsen, C.B., Fagerlin, A., Xu, Y., Presson, A. and Kaphingst, K.A. (2017). \textbf{An Intervention Aimed at Improving Decision Role Concordance in Newly Diagnosed Breast Cancer Patients.} In JOURNAL OF WOMENS HEALTH (Vol. 26, No. 9, pp. 1032-1033).
\item[22.] Elkeeb, D., Xu, Y., Presson, A., Petersen, M. and Secrest, A. (2017). \textbf{Nonmodifiable patient characteristics as predictors of patient satisfaction in dermatology.} In JOURNAL OF THE AMERICAN ACADEMY OF DERMATOLOGY (Vol. 76, No. 6, pp. AB181-AB181).
\item[23.] Keihani, S., Xu, Y., Presson, A.P., Smith, B.P., Reilly, P.M., Luo-Owen, X., Mukherjee, K., Morris, B.J., Majercik, S., Thomsen, P.B. and Erickson, B.A. (2017). \textbf{MP79-01 Nephrectomy after High-grade Renal Trauma: Results from the American Association for the Surgery of Trauma (AAST) Genitourinary Trauma Study.} The Journal of Urology, 197(4S), pp.e1072-e1073. 
\end{list1}

\section{\sc Conference proceedings}
\begin{list1}
\item[24.] Xu, Y. and Yadlowsky, S. (2022). \textbf{Calibration Error for Heterogeneous Treatment Effects.} In International Conference on Artificial Intelligence and Statistics (pp. 9280-9303) (AISTAT 2022)
\item[25.] Pfohl, S.R., Xu, Y., Foryciarz, A., Ignatiadis, N., Genkins, J. and Shah, N.H. (2022). \textbf{Net benefit, calibration, threshold selection, and training objectives for algorithmic fairness in healthcare.} Accepted by the ACM Conference on Fairness, Accountability, and Transparency (ACM FAccT 2022). 
\end{list1}

\section{\sc Preprints}
\begin{list1}
\item[26.] Xu, Y., Ignatiadis, N., Sverdrup E., Fleming S., Wager, S.,  and Shah, N. (2022). \textbf{Treatment Heterogeneity with Survival Outcomes.} Under preparation as a causal inference book chapter. \\ 
\item[27.] Xu, Y., Bechler K., Callahan A.,  and Shah, N. (2022). \textbf{Evaluating the Treatment Effect Heterogeneity of Dabigatran in Efficacy and Safety Outcomes.} Working paper. Submitted to The Journal of the American Medical Association. \\
\end{list1}


\section{\sc Software}
{\bf R packages}:
\begin{list2}
\item \href{https://github.com/som-shahlab/survlearners/tree/master/r-package/survlearners}{{\color{urlblue} survlearners}}: Metalearerns for estimating heterogeneous treatment effects for survival outcomes.
\item \href{https://github.com/CrystalXuR/CEAOptimalITR}{{\color{urlblue} CEAOptimalITR}}: Estimating the optimal individualized treatment rule (ITR) from
a cost-effectiveness perspective.
\item \href{https://github.com/CrystalXuR/EfficientCEITR}{{\color{urlblue} CEAOptimalITREfficient}}: An improved version of CEAOptimalITR, and it provides
more accurate estimates of the optimal cost-effective ITR with less variability.
\item \href{https://github.com/CrystalXuR/ECETH}{{\color{urlblue} ECETH}}: Calibration Error for Heterogeneous Treatment Effects.
\end{list2}


\section{\sc Research appointments}
\textbf{Center for Biomedical Informatics Research (BMIR)} \hfill 2020 – Present\\
Stanford University, California, USA  \\
Postdoctoral fellow, funded by the NHLBI R01 grant 'applying statistical learning tools to personalize cardiovascular treatment'. \\
\textbf{Department of Population Health Sciences (PHS)} \hfill 2018 – 2020\\
University of Utah, Utah, USA\\
Graduate assistant, funded by the R01 grant 'Optimize-SPRINT study'.\\
\textbf{Value and Epidemiology Research Using Causal Inference and Data} \hfill 2017 - 2020\\
Veteran Affairs, Salt Lake City, Utah, USA\\ 
Research assistant in the group of Prof. Brian Sauer \\
\textbf{Study Design and Biostatistics Center (SDBC)} \hfill 2016 - 2019\\
University of Utah, Utah, USA\\
Research assistant in the group of Prof. Tom Green. \\
\textbf{Department of Family and Preventive Medicine (FPMD)}  \hfill 2014 - 2016\\
University of Utah, Utah, USA\\
Research assistant in the group of Prof. Joseph Stanford. 


\section{\sc Talks and Presentations}
\textbf{Metalearners for Heterogeneous Treatment Effects on Survival Outcomes in Experiments.}   \hfill May 2022\\
American Causal Inference Conference\\
University of California, Berkeley\\
\textbf{Calibration Error for Heterogeneous Treatment Effects.} \hfill March 2022\\
International Conference on Artificial Intelligence and Statistics (AISTATS)\\
Virtual Conference\\
\textbf{A Conditional Random Forest Approach to Estimating the Most Cost-effective Individualized Treatment Rule.}  \hfill August 2021\\
Journal of Statistical Meetings, Health Policy Statistics Section \\
Virtual Conference  \\
\textbf{Estimating the Optimal Individualized Treatment Rule from A Cost-Effectiveness Perspective.} \hfill September 2019\\
American Statistical Association, Biopharmaceutical Section Regulatory-Industry Statistics Workshop Program \\
Washington D.C.\\
\textbf{Random-Forest Based Personalized Treatment Rule Optimization from A Cost-Effectiveness Perspective with An Application to the SPRINT Study.} \hfill September 2019 \\
The 3rd Annual Translational Hypertension Symposium and Early-Stage Investigator Workshop\\
University of Utah\\
\textbf{Was the Effect of Intensive Blood Pressure Intervention on CVD Risk Heterogeneous in the SPRINT Study?}  \hfill September 2018\\
The 2nd Annual Translational Hypertension Symposium and Early-Stage Investigator Workshop\\
Salt Lake City, Utah\\
\textbf{Optimal Study Design for Diagnostic Accuracy Studies: Differential Verification versus Partial Verification.} \hfill September 2017\\
Association for Clinical and Translational Science\\
Washington D.C.\\


\section{\sc Teaching}
\textbf{Teaching Assistant (TA)} at University of Utah\\
Math 5010: Introduction to Probability  \hfill Fall 2016\\ 
Math 5080: Statistics Inference I. \hfill Fall 2017\\
Math 5090: Statistics Inference II. \hfill Fall 2018

\section{\sc Peer Review}

\textbf{Statistics journals}\\

\ver

\textbf{Other journals}\\

\ver
\textbf{Conferences}\\
AISTATS 2022







\end{resume}
\end{document}
